### 2016-03-10 paper/stereo.tex
yasu

\section{Swarm Fusion implementations}
We compare our Swarm fusion methods against competing approaches over
three problems in Computer Vision. The SF architecture has high degrees
of freedom and the challenge is to properly quantity the contribution of
various algorithmic aspects. For this purpose, we carefully design the
SF architecture for each problem independently, sometimes limiting the
capabilities on purpose, to enable effective and fair comparative
evaluation.  We now explain the details of the three problems.

@@

\mysubsubsection{Swarm fusion architecture}

>>>>

\section{Swarm Fusion implementations \yasu{I don't like this title..}}
We compare our Swarm fusion methods against competing approaches over
three problems in Computer Vision. The SF architecture has high degrees
of freedom and the challenge is to properly quantity the contribution of
various algorithmic aspects. For this purpose, we carefully design the
SF architecture for each problem independently, sometimes limiting the
capabilities on purpose, to enable effective and fair comparative
evaluation.  We now explain the details of the three problems.

@@

\mysubsubsection{Swarm fusion architectures}
